Interval Probability for Fuzzy Quantum Theories

### 2016-06-15 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} updates...

Similar to the classical case, by applying the law of large number,
quantum probabilities can be estimated by relative frequencies as
well.. For example, Stern and Gerlach found a beam of silver atoms
deflects in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, two spots will be produced corresponding
to $\ket{0}$ and $\ket{1}$. In reality, we need a lot of resource
to keep the local field of strength directing to the $z$-axis, to
keep the atoms having almost the same velocity, and to point out the
exact position each particle landed on.

If the field of strength does not perfectly direct to the $z$-axis,
we does not really test the quantum event we want to test. This problem
will be handled later when we introduce the discrete quantum theory.
Even if the field of strength is perfectly direct to the $z$-axis,
the variant velocity makes spots broader and more washed out. Together
with the precision limit of the detector, it may sometimes be hard
to decide a particle corresponding to which state. For higher spins,
the bounded resource even limits the ability of entangled systems
to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$.

>>>>

Similar to the classical case, by applying the law of large number,
quantum probabilities can be estimated by relative frequencies. For
example, if we want to know the probability of the spin up in the
Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
we can put a beam of silver atoms in a highly inhomogeneous magnetic
field, and counting the number of atoms deflects up. Ideally, if the
local field strength directs to the $z$-axis, and all particles have
the same velocity, the Stern-Gerlach experiment only produces two
spots corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need
a lot of resource to keep the local field of strength directing to
the $z$-axis, to keep the atoms having almost the same velocity,
and to point out the exact position each particle landed on.

If the field of strength does not perfectly direct to the $z$-axis,
we does not really test the quantum event we want to test. This problem
will be handled later when we introduce the discrete quantum theory.
Even if the field of strength is perfectly direct to the $z$-axis,
the variant velocity makes spots broader and more washed out. Together
with the precision limit of the detector, it may sometimes be hard
to decide a particle corresponding to which state. For the Stern-Gerlach
experiment on higher spins, the bounded resource even limits the ability
of entangled systems to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$.
